scikit-image, a Python library for 2D and 3D image processing

### 2016-08-16 skimage_tomo.tex
Continued section on image processing capabilities

%%% Put your definitions there:
\startlocaldefs
\endlocaldefs

@@

Several software applications and libraries are available to synchrotron
users to process their images. ImageJ~\citep{Abramoff2004, Schneider2012}
and its distribution Fiji~\citep{Schindelin2012} is a popular tool for
2-D and 3-D images, thanks to its intuitive menus and graphical tools,
and the wealth of plugins contributed by a vivid
community~\citep{Schindelin2015}. For 3-D images, commercial tools such
as Avizo 3D software (TM) are appreciated for an intuitive graphical
pipeline and advanced 3D visualization. Alternatively, the use of a
programming language gives finer control and more possibilities, provided
classical processing algorithms can be called from libraries -- hence
limiting the programming task and the risk of bugs. Matlab (TM) and its
image processing toolbox are popular in the academic community of
computer vision and image processing. The Python language is widely used
in the scientific world and in synchrotron facilities. As a
general-purpose language, Python is used in synchrotrons to control
device servers~\citep{pytango}, to reconstruct tomography volumes from
radiographs~\citep{Gursoy2014, Mirone2014}, and in data
processing packages for macromolecular cristallography~\citep{Adams2010},
azimuthal integration of diffraction data~\citep{Ashiotis2015} or
fluorescence analysis~\citep{pymca}.

@@

>>>>

%%% Put your definitions there:
\startlocaldefs
\newcommand{\emma}[1]{{\color{blue}{#1}}}

\endlocaldefs

@@

Several software applications and libraries are available to synchrotron
users to process their images. ImageJ~\citep{Abramoff2004, Schneider2012}
and its distribution Fiji~\citep{Schindelin2012} is a popular tool for
2-D and 3-D images, thanks to its intuitive menus and graphical tools,
and the wealth of plugins contributed by a vivid
community~\citep{Schindelin2015}. For 3-D images, commercial tools such
as Avizo 3D software (TM) are appreciated for an intuitive graphical
pipeline and advanced 3D visualization. Alternatively, the use of a
programming language gives finer control and more possibilities, provided
classical processing algorithms can be called from libraries -- hence
limiting the programming task and the risk of bugs. Matlab (TM) and its
image processing toolbox are popular in the academic community of
computer vision and image processing. The Python language is widely used
in the scientific world and in synchrotron facilities. As a
general-purpose language, Python is used in synchrotrons to control
device servers~\citep{pytango}, to access raw data of X-ray
detectors~\citep{Knudsen2013}, to reconstruct tomography volumes from
radiographs~\citep{Gursoy2014, Mirone2014}, and in data
processing packages for macromolecular cristallography~\citep{Adams2010},
azimuthal integration of diffraction data~\citep{Ashiotis2015} or
fluorescence analysis~\citep{pymca}.

@@

\emma{Insert paragraph on features detection here? Juan?} Diffraction
peaks in 2D diffraction images can be extracted using blob detection
methods~\citep{Ashiotis2015}, such as the Laplacian of Gaussian method
(see Fig.~\ref{fig:tomo_gallery}).

Segmentation of regions of interest can be achieved using different
strategies, depending on the characteristics of the image. Images with a
clear contrast between regions can be segmented automatically thanks to
several thresholding algorithms, including an adaptive local thresholding
algorithm aimed at images with contrast variations. Super-pixel
algorithms~\citep{Felzenszwalb2004, Achanta2012} (see
Fig.~\ref{fig:tomo_gallery}) create an over-segmentation of images in
super-pixels, by grouping pixels that are close together both in color-
and direct space. Region-growing algorithms, such as the morphological
watershed or the random walker~\citep{Grady2006}, propagate the labels
of user-defined markers through the image (see
Fig.~\ref{fig:tomo_gallery}). The active contour
algorithm~\citep{Kass1988} fits snake contours to features of the
image, such as edges or high-brightness regions.

The characteristics of labeled regions (particles, porosities, organs,
\dots) resulting from a segmentation can be measured using the
\texttt{measure} submodule. The different connected components (e.g.
bubbles or non-touching particles) of a binary image are labeled with the
\texttt{measure.label} function. Properties of labeled regions such as
size, extent, center of mass or mean intensity value are accessed with
\texttt{measure.regionprops} (see Fig.~\ref{fig:tomo_gallery}). Local
characteristics of a region can be retrieved as well:
Fig.~\ref{fig:tomo_gallery} shows how the local diameter of open
porosity is measured by combining a skeletonization of the porosity
channels, and the distance transform to the other phase measured on the
skeleton.
